### 2011-08-06 doc/theses/vitasek/diplomka.tex
Thesis: in progress

This work will be building upon the achievements of jInfer schema inference framework, expanding its possibilities in the field of search for \textit{key-} and \textit{foreign key-}like structures in existing XML documents.

@@

The pseudocode is listed (cited from \cite{fidax} with trivial modifications) in \ref{ch-fidax}.

@@

@@

TODO we will be using jInfer and its module AttributeStats see \ref{jInfer} and \ref{attrstats}.

@@

\begin{itemize}
  \item Which construction heuristic is the best - limit GLPK to like 1 second
  \item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
  \item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
  \item Alpha, Beta -> How does the solution work?
	\item Which GLPK -> How does (time->quality) look, how does (input->time) look
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Seems that Random is better and even has smaller variance)
\end{itemize}

>>>>

This work will be building upon the achievements of jInfer schema inference framework (TODO link Anti's improvements in schema inference), expanding its possibilities in the field of search for \textit{key-} and \textit{foreign key-}like structures in existing XML documents.

@@

The pseudocode is listed (cited from \cite{fidax} with trivial modifications without changing the logic) in \ref{ch-fidax}.

@@

\section{IDREF}

TODO describe the (rather trivial) algorithm of finding IDREF attributes once we have the ID set

@@

TODO we will be using jInfer and its module AttributeStats see \ref{jInfer} and \ref{attrstats}.
TODO describe how to create a model, describe how we get IGG, link BasicIGG

@@

\begin{itemize}
	\item For each input file: how long does model creation take?
	\item How long does it take to communicate with GLPK? Creating the input/parsing the output.
	\item Which construction heuristic is the best - limit GLPK to like 1 second
	\item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
	\item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Alpha, Beta -> How does the solution work?
	\item Which GLPK -> How does (time->quality) look, how does (input->time) look
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Seems that Random is better and even has smaller variance)
\end{itemize}
